
\cvsection{Skills}
\begin{itemize}
\item \textbf{\color{black}Programming Languages}: C++ , C, HTML, JavaScript, CSS, TypeScript, Java, Golang
\end{itemize}
\begin{itemize}
\item \textbf{\color{black}Skills}: Data Structures and Algorithms (DSA) , Full Stack Web Development, .
\end{itemize}
\begin{itemize}
\item \textbf{\color{black}Libraries/Frameworks}: Node.js, React.js, ElasticSearch, Django, Flask, Android, Flutter.
\end{itemize}
\begin{itemize}
\item \textbf{\color{black}DB language}: SQL, MySQL, PostgreSQL, MongoDB, Cloud Databases 
\end{itemize}
\begin{itemize}
\item \textbf{\color{black}Tools} : Git, VScode, Jira, Azure, AWS, Google Cloud, Heroku, Kibana.
\end{itemize}
\begin{itemize}
    \item \textbf{\color{black}Coding Platform Links}: \href{https://www.leetcode.com/pratyushraj2fastandfurious/}{\color{black}\textbf{Leetcode}}, \href{https://www.hackerrank.com/2rajpratyush/}{\color{black} \textbf{Hacker Rank}},  {\href{http://www.codechef.com/users/rajpratyush23/}{\color{black}\textbf{CodeChef}}}
\end{itemize}

%\divider\smallskip

\cvsection{PROJECTS}

\begin{itemize}
\item \textbf{\color{black}NEST} using \textbf{ \color{black}Python, Streamlit, Tensorflow :} \\A web app to forecast price through visual and textual features of house. \href{https://www.github.com/rajpratyush/NEST}{\color{black}\textbf{Link}}
\item \textbf{\color{black}SpaceX } using \textbf{ \color{black}ReactJS and API :} \\Search and find any space programs launched by SpaceX with multiple filters.  \href{https://fleo-spacex-task.herokuapp.com/}{\color{black}\textbf{Live Link}}
\item \textbf{\color{black}Neuror} using \textbf{ \color{black}Java and Android:}  \\App to connect autistic personnel to recruiters. here.\href{https://www.github.com/rajpratyush/NEST}{\color{black}\textbf{Live Link}}
\item \textbf{\color{black}SoDV Detector} using \textbf{\color{black} Python \& OpenCV}\\An app that detects people in video streams using the YOLO object detection \href{https://github.com/rajpratyush/Social-Distancing-Detector/}{\color{black}\textbf{Link}}
\item \textbf{\color{black}Meeting Panda} using \textbf{\color{black} Python \& AWS }\\A Web meeting Transcription dashboard to examine meetings. \href{http://meetingpandaenv-env.eba-8jquxvpt.ap-south-1.elasticbeanstalk.com/}{\color{black}\textbf{Live Link}}
\item \textbf{\color{black}All Computer Science Engineering (CSE) Projects} - \href{https://github.com/rajpratyush}{\color{black}\textbf{Github}}.
\end{itemize}



%% Yeah I didn't spend too much time making all the 
%% spacing consistent... sorry. Use \smallskip, \medskip, 
%% \bigskip, \vpsace etc to make ajustments.
\medskip

\cvsection{ACHIEVEMENTS}

\begin{itemize}
\item Won the \textbf{1st Prize} in \textbf{2020 EMEA - Code For Good}.
\item Technical Mentor of \textbf{MLH} \& \textbf{Tech Together} Hackathons.
\item \textbf{Open Source Contributor}at \textbf{Microsoft-Graspologic, Matplotlib}.
\item \textbf{Winner} in \textbf{Pride Hacks}.
\item \textbf{Google Cloud Challenge Winner} in \textbf{Neighbourhood Hacks}.
\item \textbf{TwilioQuest Runner-up}in \textbf{Hack-Cade}.
\item 	\textbf{6 star} at \textbf{Hacker Rank} and  \textbf{3 Star} at \textbf{CodeChef with max rating of 1743}.
\item  \textbf{600+ questions} on \textbf{LeetCode}.
\item Earned \textbf{Problem Solving} Certificate from \textbf{Hacker Rank}.
\end{itemize}


